\huge A Usability Evaluation of Tor Launcher

### 2016-10-28 pets2017-paper/pets2017-paper.tex
add a placeholder image to show old interface screens, and refer to it in text.

\subsection{Procedure} 
Two researchers performed the cognitive walkthough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time. We then systematically tried action sequences from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.

@@

>>>>

\subsection{Procedure} 
Two researchers performed the cognitive walkthough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}). We systematically tried action sequences from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{placeholder-fullpage.pdf}
\caption{
A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. 
}
\label{fig:old-interface}
\end{figure*}
